R Notebook

### 2021-08-12 Paper_Figure_code.Rmd
Add files via upload

################ Methylation paper Figure ################

@@

############# 100 WB GSE132203_100 samples methylation ###############

###############   BPmet  ###################

@@

###############   MethylCIBERSORT  ##################

@@

###############   DHS  ##################

@@

############## methylation 6 WB samples GSE77797 ##############

############## BPmet ###################

@@

###################### MethylCIBERSORT_WB #########################

@@

###################### DHS #########################

@@

##########  methylation TCGA-LUAD with previous tumor purity methods ############

############## BPmetCan and MethylCIBERSORT_Luad ###################

```{r}
library(reshape2)
library(scales)
library(ggpubr)
library(EpiDISH)

load("~/Documents/Ting_paper/Code/all_figures/Figure3 and S3/Figure3_and_S3.RData")

@@

##########  methylation TCGA-BRCA with previous tumor purity methods ##########

############## BPmetCan and MethylCIBERSORT_breast ###################

@@

############################ DNA methylation lymphocytes ###################################

############################ BPmetCan ###################################

@@

############## MethylCIBERSORT #####################

@@

# Neutrophiles: Neutrophils
```{r}

@@

############## Options DHS #####################

@@

# Figure 4 and Figure S3  
```{r}

#### Figure 3 #####

@@

############################ RNAseq lymphocytes ###################################

##########  RNAseq GSE107011 PBMC Monaco ############

############## BPRNA ###################

```{r}
library(Metrics)

# load("~/deconvolution/Final methylation paper/figure/Figure4/GSE107011_PBMCs_Fig4.RData")

@@

p_melt_GSE107011_BPRNA_EpiDISH_modify_all <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify_FACS, aes(x = FACS, y = ALL, colour = cell_type)) +
  geom_point(shape = 19, size = 4) +
  theme_bw() +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
  stat_smooth(method = lm, color = "black", fullrange = T) +
  facet_wrap(~"ALL") +
  scale_x_continuous(name = NULL, limits = c(0, 0.4)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.8)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 18, color = "black") +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm")) +
  annotate("text", x = 0.3, y = 0, label = paste("R = ", round(cor.test(as.matrix(GSE107011_BPRNA_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1, 2, 4, 3, 5, 6)]))$est, 2)), parse = F, size = 8)

p_melt_GSE107011_BPRNA_EpiDISH_modify_all_longly <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify_FACS, aes(x = FACS, y = ALL, colour = cell_type)) +
  geom_point(shape = 19, size = 4) +
  theme_bw() +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
  stat_smooth(method = lm, color = "black", fullrange = T) +
  facet_wrap(~"BPRNA") +
  scale_x_continuous(name = NULL, limits = NULL) +
  scale_y_continuous(name = NULL, breaks = NULL, labels = NULL) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 18, color = "black") +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm")) +
  annotate("text", x = 0.29, y = 0.07, label = paste("R = ", round(cor.test(as.matrix(GSE107011_BPRNA_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1, 2, 4, 3, 5, 6)]))$est, 2)), parse = F, size = 8)

@@

# left = text_grob("BPRNA estimate", color = "black", size = 20, rot = 90),
```

@@

# GSE107011_PBMCs <- read.table("~/paper1.txt", row.names = 1, header = T)
# GSE107011_PBMCs_pvalue <- read.table("~/paper1.txt", row.names = 1, header = T)

@@

# Figure_4 <- ggarrange(figure_GSE107011_BPRNA_EpiDISH_together ,PBMCs_figure, ncol = 1, nrow=2, font.label = list(size = 20, color = "black"))

# ggdraw()+ draw_plot(p_GSE107011_CCLE_TIL10_EpiDISH_modify_all, x=0, y=0.6, width=0.5, height = 0.4)+
#     draw_plot(p_melt_GSE107011_BPRNA_EpiDISH_modify_all, x=0.5, y= 0.6, width=0.5, height = 0.4) +
#     draw_plot(p_melt_GSE107011_BPRNACan_EpiDISH_modify_all, x=1, y=0.6, width = 0.5, height = 0.4)+
#     draw_plot(PBMCs_figure, x=0, y= 0, width = 1, height = 0.6)+
#     draw_plot_label(label = c("a", "b", "c", "d"), size = 18, x=c(0, 0.5, 1, 0), y=c(1, 1, 1, 0.58))
#
#
# ggdraw()+ draw_plot(figure_GSE107011_all_together, x = 0.05, y = 0.5, width = 0.9, height = 0.5)+
#     draw_plot(PBMCs_figure, x=0, y= 0, width = 1, height = 0.5) +
#     draw_plot_label(label = c("a", "b"), size = 20, x = c(0.01, 0.01), y=c(1, 0.5))
#
#
# ggarrange(PBMCs_figure, labels = "b", nrow=1, ncol = 1, font.label = list(size = 20, color = "black"), widths = c(1,1))
```

######### Not Run #####

######### CCLE_TIL10 ###################

@@

############## BPRNACan ###################

@@

############## PBMC GSE107011  ###################

@@

######### Not Run #####

@@

############################ 1700 in-silico mixture RNAseq benchmark ############################

############################ CCLE_TIL10 ############################

@@

# load("/home/ting/deconvolution/Final methylation paper/figure/Figure_S4/Silico_1700_RNAseq.RData")

out.l <- epidish(silico_1700, CCLE_TIL10, "RPC", maxit = 200)
benchmarker_CCLE_TIL10 <- data.frame(out.l$estF[, c(1, 8, 9, 5, 3, 4, 2, 7, 6, 10, 11)])
benchmarker_CCLE_TIL10 <- cbind(benchmarker_CCLE_TIL10, Facs_Silico_1700)

@@

############################ BPRNACan ############################

@@

#############  H&E #####################

############## CCLE_TIL10 #####################

@@

library(reshape2)
library(scales)
library(ggpubr)
library(EpiDISH)

@@

############## BPRNACan #####################

@@

##########  RNAseq Ludo's data 59 multiple myeloma TME patients ############

############## BPRNACan ###################

@@

############## quanTIseq ###################

```{r}
library(immunedeconv)
library(textshape)
library(dplyr)

@@

######################### MCP-counter ######################################

@@

############## scRNAseq GSE72056  ###################

############## BPRNACan ###################

```{r}
library(Metrics)

@@

############## quanTIseq ###################

```{r}
library(immunedeconv)
library(textshape)

@@

############## MCP-counter ###################

@@

###################### Lymphocytes Figure_6a_b ###########################

```{r}
###################### Lymphocytes Figure_6a_b ###########################
library(cowplot)

@@

###################### Figure_6c ###########################

@@

###################### scRNA-seq melanoma Figure_6d ###########################

@@

##########  RNAseq TCGA-LUAD with previous tumor purity methods ############

############## CCLE_TIL10 and BPRNACan ###################

@@

########### BPRNACan ####################

@@

# Start Figure S6 
Test CCLE_TIL10 and BPRNACan using all public datasets (except PBMC)

@@

library(dplyr)

@@

### LUAD H&E RNAseq ###

@@

### Melanoma_GSE72056 ###

@@

### Melanoma_GSE93722 ###

>>>>

################ Methylation paper Figure

@@

############# 100 WB GSE132203_100 samples methylation

############### BPmet

@@

############### MethylCIBERSORT

@@

############### DHS

@@

############## methylation 6 WB samples GSE77797

############## BPmet

@@

###################### MethylCIBERSORT_WB

@@

###################### DHS

@@

########## methylation TCGA-LUAD with previous tumor purity methods

############## BPmetCan and MethylCIBERSORT_Luad

```{r}
load("~/Documents/Ting_paper/Code/all_figures/Figure3 and S3/Figure3_and_S3.RData")

@@

########## methylation TCGA-BRCA with previous tumor purity methods

############## BPmetCan and MethylCIBERSORT_breast

@@

############################ DNA methylation lymphocytes

############################ BPmetCan

@@

############## MethylCIBERSORT

@@

@@

############## Options DHS

@@

# Figure 4 and Figure S3

#### Figure 4 #####

@@

############################ RNAseq lymphocytes

########## RNAseq GSE107011 PBMC Monaco

############## BPRNA

```{r}
load("~/Documents/Ting_paper/Code/all_figures/Figure4/GSE107011_PBMCs_Fig4.RData")

@@

p_melt_GSE107011_BPRNA_EpiDISH_modify_all <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify_FACS, aes(x = FACS, y = ALL, colour = cell_type)) +
  geom_point(shape = 19, size = 4) +
  theme_bw() +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
  stat_smooth(method = lm, color = "black", fullrange = T) +
  facet_wrap(~"ALL") +
  scale_x_continuous(name = NULL, limits = c(0, 0.4)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.8)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 18, color = "black") +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
  annotate("text", x = 0.3, y = 0, label = paste("R = ", round(cor.test(as.matrix(GSE107011_BPRNA_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1, 2, 4, 3, 5, 6)]))$est, 2)), parse = F, size = 8)

p_melt_GSE107011_BPRNA_EpiDISH_modify_all_longly <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify_FACS, aes(x = FACS, y = ALL, colour = cell_type)) +
  geom_point(shape = 19, size = 4) +
  theme_bw() +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
  stat_smooth(method = lm, color = "black", fullrange = T) +
  facet_wrap(~"BPRNA") +
  scale_x_continuous(name = NULL, limits = NULL) +
  scale_y_continuous(name = NULL, breaks = NULL, labels = NULL) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 18, color = "black") +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
  annotate("text", x = 0.29, y = 0.07, label = paste("R = ", round(cor.test(as.matrix(GSE107011_BPRNA_EpiDISH_modify), as.matrix(FACS_GSE107011[, c(1, 2, 4, 3, 5, 6)]))$est, 2)), parse = F, size = 8)

@@

```

@@

@@

```

######### Not Run

######### CCLE_TIL10

@@

############## BPRNACan

@@

############## PBMC GSE107011

@@

######### Not Run

@@

############################ 1700 in-silico mixture RNAseq benchmark

############################ CCLE_TIL10

@@

load("~/Documents/Ting_paper/Code/all_figures/Figure_S4/Figure_S4.RData")

out.l <- epidish(Silico_1700, CCLE_TIL10, "RPC", maxit = 200)
benchmarker_CCLE_TIL10 <- data.frame(out.l$estF[, c(1, 8, 9, 5, 3, 4, 2, 7, 6, 10, 11)])
benchmarker_CCLE_TIL10 <- cbind(benchmarker_CCLE_TIL10, Facs_Silico_1700)

@@

############################ BPRNACan

@@

############# H&E

############## CCLE_TIL10

@@

@@

############## BPRNACan

@@

########## RNAseq Ludo's data 59 multiple myeloma TME patients

############## BPRNACan

@@

############## quanTIseq

@@

######################### MCP-counter

@@

############## scRNAseq GSE72056

############## BPRNACan

@@

############## quanTIseq

@@

############## MCP-counter

@@

###################### Lymphocytes Figure_6a_b

```{r}
###################### Lymphocytes Figure_6a_b ###########################

@@

###################### Figure_6c

@@

###################### scRNA-seq melanoma Figure_6d

@@

########## RNAseq TCGA-LUAD with previous tumor purity methods

############## CCLE_TIL10 and BPRNACan

@@

########### BPRNACan

@@

# Start Figure S6

Test CCLE_TIL10 and BPRNACan using all public datasets (except PBMC)

@@

@@

### LUAD H&E RNAseq

@@

### Melanoma_GSE72056

@@

### Melanoma_GSE93722
